Figures for conference paper

### 2019-05-15 conference figures COPA2019.Rmd
create file

output_folder <- "Conference/Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

@@

```{r fig_student_data}
student_data %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/student_data.pdf"))
```

@@

```{r fig_course_data}
course_data %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/course_data.pdf"))
```

@@

@@

@@

      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']

@@

      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Courses']
      }

@@

      SD -> AP [weight = 2];
      {SD, TM} -> TE;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

@@

      {AP, TE} -> x1 [arrowhead = none]
      x1 -> PM [label = '  Lasso'];

@@

      {TM, PM} -> x3 [arrowhead = none]
      x3 -> PRE [label = '  KL distance'];

@@

# Save by hand
# image format: JPEG
# Width: 626
# Check Maintain aspect ratio
# File name: Conference/Figures/Flowchart
```

@@

    labs(title = str_c("Topic ", topic),
         x = "Terms",
         y = "Beta"
         )

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

@@

```{r fig_beta}
plot_beta(1)
```

@@

    labs(title = course,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

@@

resize_factor <- 1.6

@@

transcript %>% 
  mutate(Grade = str_c(Grade, "/10")) %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))

gamma %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))

topic_expertise %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  labs(x = "Topics", y = "Topic Expertise")

ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
       width = plot_width, height = plot_height)
```

>>>>

output_folder <- "Conference/COPA2019/paper/figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

@@

```{r}
latex_table <- function(df, filename = "test"){

  df %>%
    kable("latex", booktabs = TRUE, align = "c") %>%
    write(file = str_c(output_folder, "/", filename, ".txt"))
}
```

```{r fig_student_data}
student_data %>% latex_table("data-student")
```

@@

```{r fig_course_data}
course_data %>% latex_table("course-student")
```

@@

      subgraph cluster_input {
		  color = white;

@@

      } #close input subgraph

@@

      SM [label = 'Student Model']

@@

      SUG [label = 'Course Suggestions']
      PR [label = 'Prediction Region']
      }

@@

      {SD, TM} -> SM;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> PR [label = '  Conformal Prediction'];

@@

      SM -> PM [label = '  Lasso'];

@@

@@

# Save by hand
# File name: Conference/COPA2019/paper/figures/flowchart
```

@@

    labs(title = NULL,
         x = "Terms",
         y = "Beta"
         )

  ggsave(filename = str_c("Beta-", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

@@

@@

    labs(title = NULL,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma-", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

@@

resize_factor <- 2

@@

transcript %>% 
  mutate(Grade = str_c(Grade, "/10")) %>%
  latex_table("toy-transcript")

gamma %>% latex_table("toy-gamma")

topic_expertise %>% latex_table("toy-contribution")

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  coord_flip() +
  labs(x = "Topics", y = "Topic Expertise")

ggsave(filename = str_c("toy-expertise.jpeg"), path = output_folder,
       width = plot_width, height = plot_height)
```
